Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-21 tex/paper1/paper1.tex
added in a rc file for matplotlib to control the figures across a bunch of routines.  helps maintain consistency across multiple programs
edits to the paper

\author{A. R. Inglis}
\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.
\affil{Physics Department, The Catholic University of America, Washington, DC, 20664, USA.}

@@

\section{Introduction}

The solar corona is observed to support many different oscillatory
phenomena.

Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practice of coronal seismology
began in earnest with observations of wave modes by SOHO-EIT
\citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
\citep{1999ApJ...520..880A} (see also \cite{} for more extensive
reviews of coronal seismology).  Since then, many papers have been
published describing oscillatory phenomena in the corona and their
interpretation in terms of theoretically known wave modes.

Oscillatory phenomena in the solar corona are relatively rare, both
spatially and temporally.  Two types of oscillatory motions have
received a lot of attention.  The first is known as a transverse
oscillation, since the loop motion is approximately transverse to the
extent of the loop \citep{valery}.  These motions appear to be
triggered by nearby flaring events, and are identified with the
fundamental harmonic of the kink mode of the flux tube that comprises
the coronal loop.  The second type is known as a longitudinal
oscillation, or propagating disturbance (PD).  These waves propogate
along flux tubes, and have been identified as slow mode (MHD)
magneto-acoustic waves (although alternative interpretations do exist
that do not invoke oscillatory phenomena, for example, \cite{}).

Their relative scarcity has prompted efforts to create automated
oscillation detection algorithms.

>>>>

\author{A. R. Inglis}
\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.}
\affil{Physics Department, The Catholic University of America, Washington, DC, 20664, USA.}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practice of coronal seismology
began in earnest with observations of wave modes by SOHO-EIT
\citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
\citep{1999ApJ...520..880A} (see also \cite{} for more extensive
reviews of coronal seismology).  Since then, many papers have been
published describing oscillatory phenomena in the corona and their
interpretation in terms of theoretically known wave modes.

Oscillatory phenomena in the solar corona are relatively rare, both
spatially and temporally.  Two types of oscillatory motions have
received a lot of attention.  The first is known as a transverse
oscillation, since the loop motion is approximately transverse to the
extent of the loop \citep{1999Sci...285..862N}.  These motions appear
to be triggered by nearby flaring events, and are identified with the
fundamental harmonic of the kink mode of the flux tube that comprises
the coronal loop.  The second type is known as a longitudinal
oscillation, or propagating disturbance (PD).  These waves propogate
along flux tubes, and have been identified as slow mode (MHD)
magneto-acoustic waves (although alternative interpretations do exist
that do not invoke oscillatory phenomena, for example, \cite{}).

Their scarcity on the Sun has prompted efforts to create automated
oscillation detection algorithms.  The need for an automated
oscillation detection algorithm is also exacerbated by the large and
rapidly growing amount of AIA data, which means that the amount of
data that has to be searched is large.  There have been several
attempts at designing such algorithms.  \cite{2004SoPh..223....1D}
describe the design of an automated oscillation-detection algorithm
based on the wavelet analysis. The algorithm finds significant wave
packets ranging from single to multiple wave cycles in duration, by a
wavelet power/confidence level comparison against the null hypothesis
that a given time series is Gaussian-distributed noise.  Pixels with
significant oscillatory content are grouped manually.
\cite{2007SoPh..241..397N} take a similar approach, using a
thresholded fast Fourier transform to find locations in TRACE data
that may support an oscillatory signal. The threshold level is defined
as three to four times the average FFT power; if the maximum FFT power
is above this level then the frequency at which that power occurs is
assumed to be real.  \cite{2010SoPh..264..403I} assume that an
oscillatory signal is present in each location in the datacube and then
use a Bayesian-based treatment to calculate the probability that the
frequency has a particular value.  This algorithm relies on
subtracting a background trend from the time-series being tested, and
assumes that the noise is Gaussian distributed.

The above algorithms precipitate detections based on the strength of
the signal of an oscillation on a pixel by pixel basis, and then group
these pixels together using some set of criteria.  The automated
detection algorithm of \cite{2008SoPh..248..395S} begins by
identifying candidate oscillatory regions as those that show a high
variance \citep{2003SoPh..213..103G} (under the implicit assumption
that the time-series has an approximately constant mean value).
Detections are based on wavelet filtering of these regions in all
three dimensions of the data cube simultaneously, with the implicit
assumption that the noise is Gaussian-distributed.

The algorithm of \cite{2008SoPh..252..321M} differs from the previous
algorithms: it begins by Fourier transforming the entire data cube,
and calculating the coherence of neighboring pixels in narrow
frequency bands, and filtering the results. The null hypothesis here
is that the time series is pure Gaussian noise, with the additional
assumption that pairs of noisy time-series have low coherence, and so
can be rejected.  In this algorithm, the spatial extent of the
coherence of the oscillatory signal is the key identifier of a wave
process.

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and at least
approximately Gaussian-distributed noise.  However, it is shown below
that time-series of coronal emission may be better described by other
models.  These models have implications for the practice of coronal
seismology, and may be indicative of the nature of the fundamental
energy deposition that keeps the corona hot.
